Some examples in extended logic counting classes

### 2015-09-01 tex/examples.tex
1 sep

\subsection{{\sc \#3-DNF}}
A function $f:\Truc \to \N$ is in $\Eone$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\Y,\y)$ such that $f = f_{\varphi(\Y,\y)}$. We will now show that {\sc \#3-DNF} $\in\Eone$.\\

@@

\subsection{{\sc \#3-HORN-SAT}}
A function $f:\Truc \to \N$ is in $\Etwo$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x,\Y,\y)$ such that $f = f_{\forall \x\,\varphi(\x,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#3-HORN-SAT} $\in\Etwo$.\\

@@

\subsection{{\sc \#DNF}}
A function $f:\Truc \to \N$ is in $\Ethree$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x^1,\x^2,\Y,\y)$ such that $f = f_{\exists\x^1\forall \x^2\,\varphi(\x^1,\x^2,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#DNF} $\in\Ethree$.

@@

\subsection{{\sc \#HORN-SAT}}
A function $f:\Truc \to \N$ is in $\Efour$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x^1,\x^2,\Y,\y)$ such that $f = f_{\forall\x^1\exists \x^2\,\varphi(\x^1,\x^2,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#DNF} $\in\Ethree$.

>>>>

\subsection{{\sc \#3-DNF}}
A function $f:\Truc \to \N$ is in $\EoneE$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\Y,\y)$ such that $f = f_{\varphi(\Y,\y)}$. We will now show that {\sc \#3-DNF} $\in\EoneE$.\\

@@

\subsection{{\sc \#3-HORN-SAT}}
A function $f:\Truc \to \N$ is in $\EoneU$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x,\Y,\y)$ such that $f = f_{\forall \x\,\varphi(\x,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#3-HORN-SAT} $\in\EoneU$.\\

@@

\subsection{{\sc \#DNF}}
A function $f:\Truc \to \N$ is in $\EtwoE$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x^1,\x^2,\Y,\y)$ such that $f = f_{\exists\x^1\forall \x^2\,\varphi(\x^1,\x^2,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#DNF} $\in\EtwoE$.

@@

\subsection{{\sc \#HORN-SAT}}
A function $f:\Truc \to \N$ is in $\EtwoU$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x^1,\x^2,\Y,\y)$ such that $f = f_{\forall\x^1\exists \x^2\,\varphi(\x^1,\x^2,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#DNF} $\in\EtwoE$.
